### 2017-03-16 thesis/latex/thesis.tex
Thesis: small commit.

\subsection{Necessary and sufficient criteria for motion}
Each of the models described above postulates a series of chemical events which occur during the dynein step. Testing such hypotheses can be done in a variety of ways.

\subsubsection{Our model}
what we're trying to do with our project

\subsubsection{Goals}
What we hope to gain by simulating such a model, and what it would contribute to the current literature

@@

@@

\paragraph{Angular and Cartesian velocities}
The goal is to express angular velocities $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$ in terms of known quantities. To begin, the cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner:

\noindent\begin{minipage}{0.49\linewidth}
\begin{align}
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \label{cartesian-bmx}\\
  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\begin{align}                                                                          
  \dot{Y}_{bb} &= 0 \\                                                        
  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}
\end{minipage}
\vspace{.5cm}

@@

\begin{align}  
  \dot{X}_{bm} &= \frac{1}{\gamma_m} \Big(F_{xml} + - \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml} \label{brownian-bmx}\\
  \dot{X}_{t } &= \frac{1}{\gamma_t} \Big(F_{xt } + - \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{fm} &= \frac{1}{\gamma_m} \Big(F_{xmr} + - \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
  \dot{X}_{fb} &= \frac{1}{\gamma_b} \Big(F_{xbr} + - \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{bm} &= \frac{1}{\gamma_m} \Big(F_{yml} + - \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma_t} \Big(F_{yt } + - \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{fm} &= \frac{1}{\gamma_m} \Big(F_{ymr} + - \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
  \dot{Y}_{fb} &= \frac{1}{\gamma_b} \Big(F_{ybr} + - \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ybr}
\end{align}

@@

These two sets of equations, cartesian and Brownian, can be equated to get more interesting equations. For example, Eq (\ref{cartesian-bmx}) and Eq (\ref{brownian-bmx}) can be equated. This equating, combined with expanding the recursive velocity definitions leads to:

\begin{align}
  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} = \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \label{ob_system_first}\\
  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx} \\
  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
\end{align}

\begin{align}
  &L_s\cos(\theta_{bb})\dot{\theta}_{bm} = \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
  &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
\end{align}

These eight equations form a system of equations with eight unknowns: $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$, and the four tension coefficients $\lambda_{bs}, \lambda_{bt}, \lambda_{um}$ and $\lambda_{ub}$. This system is more compactly represented as:
{\small
  \[
  \hspace{-1.0cm}
  \resizebox{0.85\linewidth}{!}{%
  $\begin{pmatrix}
    L_s\sin\theta_{bb} & 0 & 0 & 0 & -\gamma_m (X_{bm} - X_{bb}) & \gamma_m (X_{t } - X_{bm}) & 0 & 0\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (X_{t } - X_{bm}) & \gamma_t (X_{um} - X_{t }) & 0\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (X_{um} - X_{t }) & \gamma_m (X_{ub} - X_{um})\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & -L_s\sin(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (X_{ub} - X_{um})\\
    -L_s\cos(\theta_{bb}) & 0 & 0 & 0 & -\gamma_m (Y_{bm} - Y_{bb}) & \gamma_m (Y_{t } - Y_{bm}) & 0 & 0\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (Y_{t } - Y_{bm}) & \gamma_t (Y_{um} - Y_{t }) & 0\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (Y_{um} - Y_{t }) & \gamma_m (Y_{ub} - Y_{um})\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & L_s\cos(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (Y_{ub} - Y_{um})\\
  \end{pmatrix}$%
  }
  \begin{pmatrix}
    \dot{\theta}_{bb}\\
    \dot{\theta}_{bm}\\
    \dot{\theta}_{um}\\
    \dot{\theta}_{ub}\\
    \lambda_{bs}\\
    \lambda_{bt}\\
    \lambda_{ut}\\
    \lambda_{us}\\
  \end{pmatrix}
  =
  \begin{pmatrix}
    -F_{bmx} + \gamma_m R_{bmx}\\
    -F_{tx} + \gamma_t R_{tx}\\
    -F_{umx} + \gamma_m R_{umx}\\
    -F_{ubx} + \gamma_b R_{ubx}\\
    -F_{bmy} + \gamma_m R_{bmy}\\
    -F_{ty} + \gamma_t R_{ty}\\
    -F_{umy} + \gamma_m R_{umy}\\
    -F_{uby} + \gamma_b R_{uby}\\
  \end{pmatrix}
  \]
}

This matrix is then solved using the Mathematica computer algebra system, resulting in a set of $\dot{\Theta}_n$ equations shown in Appendix (\ref{ob-motion-equations]}).

@@

These values are arrived at through the Law of Cosines and a trigonometric identity. The sign of $\sin\left(\Theta_n\right)$ is restricted to positive values due to the angle's $[0,\pi]$ domain. $\Theta_{ns}$'s domain is $[-\pi,\pi]$, meaning its sign is not restricted. The partial derivatives of these values are useful:

\begin{align}
  \frac{\partial \cos\theta_n}{\partial L_n} &= \frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\\
  \frac{\partial \cos\theta_n}{\partial L_f} &= -\frac{L_f}{LL_n}\\
  \frac{\partial \sin\theta_n}{\partial L_n} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
  \left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)\\
  \frac{\partial \sin\theta_n}{\partial L_f} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
  \left(\frac{-L_f}{LLn}\right)\\
  \frac{\partial \cos\theta_{ns}}{\partial L_n} &= \frac{1}{L_s}
  - \frac{L_s^2 + L_n^2 - L_t^2}{2L_sL_n^2}\\
  \frac{\partial \cos\theta_{ns}}{\partial L_f} &= 0\\
  \frac{\partial \sin\theta_{ns}}{\partial L_n} &=
  \begin{cases}
    \frac{-\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} < \pi \\
    \frac{\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} > \pi
  \end{cases}\\
  \frac{\partial \sin\theta_{ns}}{\partial L_f} &= 0
\end{align}

@@

The partial derivatives of these values are:

\begin{align}
  \frac{dX_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}\Big)\\
  \frac{dY_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_n} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_n} \Big)\\
  \frac{dX_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f} \Big)\\
  \frac{dY_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_f} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}\Big)\\
  \frac{dX_{t}}{dL_n} &= \cos\theta_n + L_n\frac{\partial \cos\theta_n}{\partial L_n} = \frac{L_n}{L}\\
  \frac{dY_{t}}{dL_n} &= \sin\theta_n + L_n\frac{\partial \sin\theta_n}{\partial L_n}\\
  \frac{dX_{t}}{dL_f} &= L_n\frac{\partial \cos\theta_n}{\partial L_f} = -\frac{L_f}{L}\\
  \frac{dY_{t}}{dL_f} &= L_n\frac{\partial \sin\theta_n}{\partial L_f}\\
\end{align}

@@

This system of equations is then solved and used to calculate $\dot{L}_n$ and $\dot{L}_f$, as shown in Appendix (\ref{both-motion-equations}).

@@

\paragraph{Euler’s method}
Show how Euler's method is arrived at, how its error scales, why we use it.

\paragraph{Vs other methods (Runge Kutta, etc)}
Talk about why our differential equation is most conducive to Euler's method. Euler's is more
efficient -- is there a way to show how our differential equation is smooth, not jagged?

@@

\begin{align}
  L_n^2 &= \left(X_t - X_{nb}\right)^2 + Y_t^2\\
  L_f^2 &= \left(X_t - X_{fb}\right)^2 + Y_t^2\\
  \cos(\Theta_{nm}) = \frac{L_s^2 + L_t^2 - L_n^2}{2L_sL_t}\\
  \cos(\Theta_{fm}) = \frac{L_s^2 + L_t^2 - L_f^2}{2L_sL_t}\\
\end{align}

@@

\subsubsection{Forces}
Spring and Brownian forces are used to properly move the model through time. Appendices (\ref{onebound-motion-equatons}-\ref{bothbound-motion-equations}) show angular velocities are functions of the x- and y-components of both spring forces $F$ and Brownian forces $\gamma R$.

>>>>

%% \subsection{Brownian dynamics}
%% New section which describes how BD works.

\subsection{This work}
\subsubsection{Necessary and sufficient criteria for motion}
One of the principle goals of researchers studying the dynein motor is establishing how it walks. This can be a difficult task, since direct observation of the motor walking is not currently experimentally possible. The next best thing, then, is building a model which both only does all the things dynein does, and generates motion. Finding such a system would be very useful for forming hypotheses on how dynein walks. Another requirement of the system would be that it be as simple as possible while still explaining all the data. By Occam's Razor, such systems are the most likely to represent real dynein. Thus, finding the necessary and sufficient criteria for dynein's motion is a big goal in the field.\\

A good starting place for finding the minimum set of motile criteria would be preexisting models, like the Cianfrocco model. This model describes a set of states which logically lead to each other and are supported by experiment. It seems intuitive that a motor which obeyed the Cianfrocco cycle would walk. There are multiple ways to verify this. A completely synthetic biological motor could be designed which obeys the cycle, and its motile properties could be studied. This seems incredibly difficult. Much easier would be to create a physical model of such a cycle, simulate it, and see if it obeys similarly to experimentally observed dynein. If the physical model both behaves according to the laws of physics and captures experimental dynein behavior well, this would be good evidence that such a model describes how dynein actually walks.\\

\subsubsection{Goals}
The goal of this work is to construct a minimum physical model of dynein protein based on the theoretical Cianfrocco model. The model should behave as physics predicts a protein to behave; namely, it should obey Brownian dynamics and conservation of energy. It should also roughly capture the state transitions and conformation changes of the Cianfrocco model. Also the model should be as simple as possible, to assure that each part of the model is necessary. If too many extra features are added, the model will not be minimal and not achieve its purpose.\\

This model will then be converted into a computer program, tested for compliance with the laws of physics, and simulated. Information on the long-term behavior of such a simulation will then be used to evaluate how well the model describe's experimental dynein's behavior.\\

@@

\textbf{todo: Add springs to joints!}

@@

\paragraph{Angular and Cartesian velocities}
The goal is to express angular velocities $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$ in terms of known quantities. To begin, the cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner. A subset of the equations are shown here:

\noindent\begin{minipage}{0.49\linewidth}
\begin{align}
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \label{cartesian-bmx}\\
  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm}
  %% \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
  %% \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\begin{align}                                                                          
  \dot{Y}_{bb} &= 0 \\                                                        
  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
  %% \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
  %% \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}
\end{minipage}
\vspace{.5cm}

@@

\begin{align}  
  \dot{X}_{bm} &= \frac{1}{\gamma_m} \Big(F_{xml} + - \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml} \label{brownian-bmx}\\
  \dot{X}_{t } &= \frac{1}{\gamma_t} \Big(F_{xt } + - \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
  %% \dot{X}_{fm} &= \frac{1}{\gamma_m} \Big(F_{xmr} + - \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
  %% \dot{X}_{fb} &= \frac{1}{\gamma_b} \Big(F_{xbr} + - \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xbr}
\end{align}

%% \begin{align}  
%%   \dot{Y}_{bm} &= \frac{1}{\gamma_m} \Big(F_{yml} + - \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
%%   \dot{Y}_{t}  &= \frac{1}{\gamma_t} \Big(F_{yt } + - \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
%%   \dot{Y}_{fm} &= \frac{1}{\gamma_m} \Big(F_{ymr} + - \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
%%   \dot{Y}_{fb} &= \frac{1}{\gamma_b} \Big(F_{ybr} + - \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ybr}
%% \end{align}

@@

These two sets of equations, cartesian and Brownian, can be equated to get more interesting equations. For example, Eq (\ref{cartesian-bmx}) and Eq (\ref{brownian-bmx}) can be equated. This equating, combined with expanding the recursive velocity definitions leads to new equations, some of which are shown here:

\begin{align}
  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} = \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \label{ob_system_first}\\
  &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx}
  %% &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
  %% &-L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
\end{align}

%% \begin{align}
%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bm} = \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} = \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} = \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
%%   &L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} = \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby} \label{ob_system_last}
%% \end{align}

A total of eight coupled differential equations are formed from this procedure. These eight equations form a system of equations with eight unknowns: $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$, and the four tension coefficients $\lambda_{bs}, \lambda_{bt}, \lambda_{um}$ and $\lambda_{ub}$. This system is more compactly represented as:
{\small
  \[
  \hspace{-1.0cm}
  \resizebox{0.85\linewidth}{!}{%
  $\begin{pmatrix}
    L_s\sin\theta_{bb} & 0 & 0 & 0 & -\gamma_m (X_{bm} - X_{bb}) & \gamma_m (X_{t } - X_{bm}) & 0 & 0\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (X_{t } - X_{bm}) & \gamma_t (X_{um} - X_{t }) & 0\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (X_{um} - X_{t }) & \gamma_m (X_{ub} - X_{um})\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & -L_s\sin(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (X_{ub} - X_{um})\\
    -L_s\cos(\theta_{bb}) & 0 & 0 & 0 & -\gamma_m (Y_{bm} - Y_{bb}) & \gamma_m (Y_{t } - Y_{bm}) & 0 & 0\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (Y_{t } - Y_{bm}) & \gamma_t (Y_{um} - Y_{t }) & 0\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (Y_{um} - Y_{t }) & \gamma_m (Y_{ub} - Y_{um})\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & L_s\cos(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (Y_{ub} - Y_{um})\\
  \end{pmatrix}$%
  }
  \begin{pmatrix}
    \dot{\theta}_{bb}\\
    \dot{\theta}_{bm}\\
    \dot{\theta}_{um}\\
    \dot{\theta}_{ub}\\
    \lambda_{bs}\\
    \lambda_{bt}\\
    \lambda_{ut}\\
    \lambda_{us}\\
  \end{pmatrix}
  =
  \begin{pmatrix}
    -F_{bmx} + \gamma_m R_{bmx}\\
    -F_{tx} + \gamma_t R_{tx}\\
    -F_{umx} + \gamma_m R_{umx}\\
    -F_{ubx} + \gamma_b R_{ubx}\\
    -F_{bmy} + \gamma_m R_{bmy}\\
    -F_{ty} + \gamma_t R_{ty}\\
    -F_{umy} + \gamma_m R_{umy}\\
    -F_{uby} + \gamma_b R_{uby}\\
  \end{pmatrix}
  \]
}

This matrix is then solved using the Mathematica computer algebra system, resulting in a set of motion equations which describe the model's trajectory over time, eg $\dot{\Theta_{bm}}(\Theta_{bb}, \Theta_{bm}, \Theta_{um}, \Theta_{ub})$. These motion equations are further described in (\ref{sec:ob-motion-equations}).\\

@@

These values are arrived at through the Law of Cosines and a trigonometric identity. The sign of $\sin\left(\Theta_n\right)$ is restricted to positive values due to the angle's $[0,\pi]$ domain. $\Theta_{ns}$'s domain is $[-\pi,\pi]$, meaning its sign is not restricted. The partial derivatives of these values are used in future calculations, and some are shown here:

\begin{align}
  \frac{\partial \cos\theta_n}{\partial L_n} &= \frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\\
  \frac{\partial \cos\theta_n}{\partial L_f} &= -\frac{L_f}{LL_n}\\
  \frac{\partial \sin\theta_n}{\partial L_n} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
  \left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)
  %% \frac{\partial \sin\theta_n}{\partial L_f} &= \frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
  %% \left(\frac{-L_f}{LLn}\right)\\
  %% \frac{\partial \cos\theta_{ns}}{\partial L_n} &= \frac{1}{L_s}
  %% - \frac{L_s^2 + L_n^2 - L_t^2}{2L_sL_n^2}\\
  %% \frac{\partial \cos\theta_{ns}}{\partial L_f} &= 0\\
  %% \frac{\partial \sin\theta_{ns}}{\partial L_n} &=
  %% \begin{cases}
  %%   \frac{-\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
  %%   \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} < \pi \\
  %%   \frac{\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
  %%   \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right) & \theta_{nm} > \pi
  %% \end{cases}\\
  %% \frac{\partial \sin\theta_{ns}}{\partial L_f} &= 0
\end{align}

@@

The partial derivatives of these values are used later. A selection are shown here:

\begin{align}
  \frac{dX_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}\Big)\\
  \frac{dY_{nm}}{dL_n} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_n} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_n} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_n} \Big)\\
  \frac{dX_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f} - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f} \Big)\\
  %% \frac{dY_{nm}}{dL_f} &= L_s\Big(\cos\theta_n\frac{d\sin\theta_{ns}}{dL_f} + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f} + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}\Big)\\
  %% \frac{dX_{t}}{dL_n} &= \cos\theta_n + L_n\frac{\partial \cos\theta_n}{\partial L_n} = \frac{L_n}{L}\\
  %% \frac{dY_{t}}{dL_n} &= \sin\theta_n + L_n\frac{\partial \sin\theta_n}{\partial L_n}\\
  %% \frac{dX_{t}}{dL_f} &= L_n\frac{\partial \cos\theta_n}{\partial L_f} = -\frac{L_f}{L}\\
  %% \frac{dY_{t}}{dL_f} &= L_n\frac{\partial \sin\theta_n}{\partial L_f}\\
\end{align}

@@

This system of equations is then solved and used to calculate $\dot{L}_n$ and $\dot{L}_f$, as shown in Appendix (\ref{sec:bb-motion-equations}).

@@

%% \paragraph{Euler’s method}
%% Show how Euler's method is arrived at, how its error scales, why we use it.

%% \paragraph{Vs other methods (Runge Kutta, etc)}
%% Talk about why our differential equation is most conducive to Euler's method. Euler's is more
%% efficient -- is there a way to show how our differential equation is smooth, not jagged?

@@

\begin{align}
  L_n^2 &= \left(X_t - X_{nb}\right)^2 + Y_t^2\\
  L_f^2 &= \left(X_t - X_{fb}\right)^2 + Y_t^2\\
  \cos(\Theta_{nm}) &= \frac{L_s^2 + L_t^2 - L_n^2}{2L_sL_t}\\
  \cos(\Theta_{fm}) &= \frac{L_s^2 + L_t^2 - L_f^2}{2L_sL_t}
\end{align}

@@

\subsubsection{Forces}
Spring and Brownian forces are used to properly move the model through time. Appendices (\ref{sec:ob-motion-equatons}-\ref{sec:bb-motion-equations}) show angular velocities are functions of the x- and y-components of both spring forces $F$ and Brownian forces $\gamma R$.
